Hydras \& Co.

### 2022-02-28 doc/gaia-chapter.tex
fix minor typos

\subsection{Canonical sequences}

In~\href{../theories/html/gaia_hydras.GCanon.html}%
{\texttt{gaia\_hydras.GCanon}}, canonical sequences are just imported from the library \linebreak
\href{../theories/html/hydras.Epsilon0.Canon.html}%
{\texttt{hydras.Epsilon0.Canon}}.
First, we rename \HydrasLib' \texttt{canon} function into
\texttt{hcanon}. Then we define a new function \emph{via} the
translations \texttt{g2h} and \texttt{h2g}.

@@

>>>>

\subsection{Canonical sequences}
Canonical sequences are described in Chapter~\vref{chap:ketonen}, and implemented in
\href{../theories/html/hydras.Epsilon0.Canon.html}%
{\texttt{hydras.Epsilon0.Canon}}.
Module~\href{../theories/html/gaia_hydras.GCanon.html}%
{\texttt{gaia\_hydras.GCanon}}, imports definitions and results from that library.

First, we rename \HydrasLib' \texttt{canon} function into
\texttt{hcanon}. Then we define a new function \emph{via} the
translations \texttt{g2h} and \texttt{h2g}.

@@

Please refer to Sect.~\ref{sect:pathes-intro} for a descrition of that library.
